# OSM building heights in Briston

```{r load}
devtools::load_all ("../../osmdata", export_all = FALSE)
library (magrittr)
```

## Resdiential buildings

```{r load-bristol-buildings-res}
bb <- opq ('Bristol UK') %>% 
    add_feature (key = 'building', value = 'residential') %>%
    osmdata_sf ()
```
Only relevant objects are polygons, although there are also 3 multipolygons, but
these only contain generic default info (name, address, geometry): 
```{r}
names (bb$osm_multipolygons)
```
In contrast,
```{r}
dim (bb$osm_polygons)
names (bb$osm_polygons)
```
has `building.levels`. There are, however, only 9 out of 1,500 buildings that
have this information, rendering it useless:
```{r}
table (bb$osm_polygons$building.levels)
sum (table (bb$osm_polygons$building.levels))
```

## Commerical buildings

```{r load-bristol-buildings-com}
bc <- opq ('Bristol UK') %>% 
    add_feature (key = 'building', value = 'commercial') %>%
    osmdata_sf ()
```
```{r}
dim (bc$osm_polygons)
names (bc$osm_polygons)
table (bc$osm_polygons$building.levels)
sum (table (bc$osm_polygons$building.levels))
```
Slightly more bulidings with specified levels, but still not enough to be
useful. And unforuntely only one building with `height` value:
```{r}
table (bc$osm_polygons$height)
```
So unfortunately, heights of commerical buildings can also not be extracted.

## Industrial buildings

```{r load-bristol-buildings-ind}
bi <- opq ('Bristol UK') %>% 
    add_feature (key = 'building', value = 'industrial') %>%
    osmdata_sf ()
```
```{r}
dim (bi$osm_polygons)
names (bi$osm_polygons)
table (bi$osm_polygons$building.levels)
sum (table (bi$osm_polygons$building.levels))
```
Building levesl are again useless, and there are no heights at all.
